\textbf{Discrete Bulk Reconstruction Problem} \\ \large Compiled Research

### 2025-03-07 paper.tex
Added text

    \subsection{CFT (Conformal Field Theory) Space $\Rightarrow$ The Boundary}
    \begin{itemize}
        \item The \textbf{Boundary} represents a lower-dimensional space the forms "edge" or "boundary" of AdS bulk.
        \item \textbf{Non-gravitational} theory that lives on the boundary of the AdS spacetime.
        \item The information of boundary is encoded in the bulk.
    \end{itemize}

    %% Photo of AdS/ CFT space 
    \begin{figure}[htbp]  % 'h' places the figure "here" (can be adjusted)
        \centering
        \includegraphics[width=0.8\textwidth]{ads_cft.jpeg}  % Adjust width as needed
        \caption{This illustration shows the AdS/CFT spacetime. Where a geodesic is a straight line across the hyperbolic disk, which is the shortest path between points. In the context of anti-de Sitter spacetime a geodesic represents the path that a particle follows when only affected by gravity.}  % Caption text
        \label{fig:AdS/CFT space}  % Label for referencing
    \end{figure}

]
    \newpage
    When dealing with a 5-dimensional AdS bulk, the boundary is typically 4-dimensional, and the CFT lives on this 4-dimensional boundary. 
    This illustrates the idea that the boundary is one dimension less than the bulk. The boundary is where we will make our computations. Because of the lack of gravity, it is easier to compute and understand. We can then use the CFT computations to reconstruct the gravitational dynamics of the AdS bulk, which translates to the geodesics of the hyperbolic disk. Geodesics in AdS space are curved, unlike straight lines in flat geometry, even though they represent the shortest path between points. This curvature reflects the negative curvature of the AdS space and the effects of gravity.
    These gravitational dynamics come from the entanglement entropy in the CFT. In AdS/CFT, entanglement entropy on the boundary CFT encodes information about the geometry of the bulk. Given a CFT state, we can determine the corresponding spacetime that the CFT describes, including its geometry and gravitational dynamics. This allows us to extract bulk information, such as spacetime curvature, directly from the boundary CFT state. Thus, we can use the CFT to reconstruct the AdS bulk.

    \textbf{AdS/CFT correspondence} means that the gravitational theory in the bulk is equivalent to the non-gravitational CFT on the boundary. In other words, the two theories describe the same physics but from different perspectives, one being a gravitational theory and the other a quantum field theory without gravity. This is an extraordinary idea because it suggests that gravity can be understood in terms of a simpler quantum field theory on the boundary, offering insights into quantum gravity through non-gravitational methods.

    \subsection{Holographic Principle}
    The \textbf{Holographic Principle} is central to the AdS/CFT correspondence.  It states that a lower-dimensional, non-gravitational theory (CFT) can fully describe the physics of a higher-dimensional gravitational theory (AdS). More formally, this principle suggests that the physics within a region of space can be described by a theory defined on the boundary of that region, with no need for the bulk to be independently described.
    \\ 
    This discovery is important because it suggests that quantum gravity, which typically involves understanding the behavior of spacetime and gravity in the bulk, can be described by a simpler theory on the boundary. In this context, we don't need to deal directly with quantum gravity in the bulk; instead, we can use quantum field theory on the boundary, which does not involve gravity. This provides a new framework for studying gravitational phenomena without having to directly engage with the complexities of quantum gravity.    \\
    \\
    \textbf{Holographic Relationship} means that everything happening in the bulk AdS spacetime can be described by the boundary CFT, and vice versa. The idea is that the bulk gravitational dynamics are encoded in the CFT through entanglement and other quantum information properties, while the CFT state encapsulates all the physics of the bulk region.
    \\
    Holographic Relationship consists of two theories:
    \begin{itemize}
        \item A theory of quantum gravity (the AdS bulk) and a quantum field theory without gravity (the CFT boundary). The relationship between the two theories is called "holographic," which is where the term "holographic relationship" comes from.
        \item Note: The equivalence of these theories is still a subject of ongoing research and has not yet been fully proven in all generalities. The mapping between the two theories has yet to be completely developed, and much of the work involves finding more specific correspondences between the two
    \end{itemize}

@@

    \subsection{Spacetime geometry and what it means in AdS/CFT space}
        \hspace{.5cm} Gravity is a curvature of spacetime caused by mass and energy. "geometry" of spacetime refers to this curve. If there is no gravity geometry is simple and uncurved.
        \\
        \indent In AdS space, geometry is negatively curved. This is because of the nature of its spacetime structure. This leads to a spacetime geometry that is "hyperbolic" in nature, meaning that it has a negative curvature at every point.
        \textbf{The CFT can reconstruct the geometry of AdS bulk}, meaning that data from the CFT can be used to determine the shape or curvature of spacetime in the AdS bulk.
        \\
        \\
        \textbf{Entanglement is directly related to geometry of the bulk spacetime}:
        \begin{enumerate}
            \item Amount of entanglement in different regions of CFT tells us about structure and curvature of the corresponding bulk spacetime in AdS.
            \item More entanglement on the boundary implies more curvature or structure in the bulk geometry.
            \item Proven with RT formula: more entanglement = larger minimal surface area = more curved and intricate bulk geometry.
        \end{enumerate}

    \subsection{Why is this important?}
        \hspace{.5cm} The shape of spacetime tells us how gravity behaves. If we can reconstruct the bulk geometry from the CFT< we can gain insights intot he quantum aspects of gravity and understand how measurements (or experiments) on the boundary affect the information encoded in the bulk.

>>>>

    \subsection{CFT (Conformal Field Theory) Space $\Rightarrow$ The Boundary}
        \begin{itemize}
            \item The \textbf{boundary} represents a lower-dimensional space that forms the "edge" or "boundary" of the AdS bulk.
            \item The \textbf{CFT} is a non-gravitational theory that lives on the boundary of the AdS spacetime.
            \item The information of the boundary is encoded in the bulk. The bulk and boundary are related by the holographic principle.
        \end{itemize}

        %% Photo of AdS/ CFT space 
        \begin{figure}[htbp]
            \centering
            \includegraphics[width=0.8\textwidth]{ads_cft.jpeg}  
            \caption{This illustration shows the AdS/CFT spacetime. A geodesic is a straight line across the hyperbolic disk, which is the shortest path between points. In the context of anti-de Sitter spacetime, a geodesic represents the path that a particle follows when only affected by gravity.}  
            \label{fig:AdS/CFT space}  
        \end{figure}

        \newpage
        When dealing with a 5-dimensional AdS bulk, the boundary is typically 4-dimensional, and the CFT lives on this 4-dimensional boundary. This illustrates the idea that the boundary is one dimension less than the bulk. The boundary is where we will perform our computations, as it is easier to compute without gravity. Using the CFT, we can reconstruct the gravitational dynamics of the AdS bulk, which corresponds to the geodesics of the hyperbolic disk. Geodesics in AdS space are curved, unlike straight lines in flat geometry, even though they represent the shortest path between points. This curvature reflects the negative curvature of AdS space and the effects of gravity.

        These gravitational dynamics come from the entanglement entropy in the CFT. In AdS/CFT, the entanglement entropy on the boundary CFT encodes information about the geometry of the bulk. Given a CFT state, we can determine the corresponding spacetime that the CFT describes, including its geometry and gravitational dynamics. This allows us to extract bulk information, such as spacetime curvature, directly from the boundary CFT state. Thus, we can use the CFT to reconstruct the AdS bulk.

        \textbf{AdS/CFT correspondence} means that the gravitational theory in the bulk is equivalent to the non-gravitational CFT on the boundary. In other words, the two theories describe the same physics but from different perspectives: one is a gravitational theory, and the other is a quantum field theory without gravity. This is an extraordinary idea because it suggests that gravity can be understood in terms of a simpler quantum field theory on the boundary, offering insights into quantum gravity through non-gravitational methods.

    \subsection{Holographic Principle}
        The \textbf{Holographic Principle} is central to the AdS/CFT correspondence. It states that a lower-dimensional, non-gravitational theory (CFT) can fully describe the physics of a higher-dimensional gravitational theory (AdS). More formally, this principle suggests that the physics within a region of space can be described by a theory defined on the boundary of that region, without the need to describe the bulk independently.

        This discovery is important because it suggests that quantum gravity, which typically involves understanding the behavior of spacetime and gravity in the bulk, can be described by a simpler theory on the boundary. In this context, we don't need to deal directly with quantum gravity in the bulk; instead, we can use quantum field theory on the boundary, which does not involve gravity. This provides a new framework for studying gravitational phenomena without directly engaging with the complexities of quantum gravity.

        \textbf{Holographic Relationship} means that everything happening in the bulk AdS spacetime can be described by the boundary CFT, and vice versa. The idea is that the bulk gravitational dynamics are encoded in the CFT through entanglement and other quantum information properties, while the CFT state encapsulates all the physics of the bulk region.

        The holographic relationship consists of two theories:
        \begin{itemize}
            \item A theory of quantum gravity (the AdS bulk) and a quantum field theory without gravity (the CFT boundary). The relationship between the two theories is called "holographic," which is where the term "holographic relationship" comes from.
            \item \textbf{Note:} The equivalence of these theories is still a subject of ongoing research and has not yet been fully proven in all generalities. The mapping between the two theories has yet to be completely developed, and much of the work involves finding more specific correspondences between the two.
        \end{itemize}

@@

    \subsection{Spacetime Geometry and What It Means in AdS/CFT Space}
        \hspace{0.5cm} Gravity is the curvature of spacetime caused by mass and energy. The "geometry" of spacetime refers to this curvature. If there is no gravity, the geometry is simple and uncurved.

        In AdS space, geometry is negatively curved due to the nature of its spacetime structure. This leads to a spacetime geometry that is "hyperbolic," meaning it has negative curvature at every point. The CFT can reconstruct the geometry of the AdS bulk, meaning that data from the CFT can be used to determine the shape or curvature of spacetime in the AdS bulk.

        \textbf{Entanglement is directly related to the geometry of the bulk spacetime:}
        \begin{enumerate}
            \item The amount of entanglement in different regions of the CFT tells us about the structure and curvature of the corresponding bulk spacetime in AdS.
            \item More entanglement on the boundary implies more curvature or structure in the bulk geometry.
            \item Proven with the RT formula: more entanglement = larger minimal surface area = more curved and intricate bulk geometry.
        \end{enumerate}

    \subsection{Why Is This Important?}
        \hspace{0.5cm} The shape of spacetime tells us how gravity behaves. If we can reconstruct the bulk geometry from the CFT, we can gain insights into the quantum aspects of gravity and understand how measurements (or experiments) on the boundary affect the information encoded in the bulk. This could lead to a deeper understanding of quantum gravity and its connection to quantum field theory.
